### 2019-04-30 reports/thesis/chapters/1_literatureReview.tex
Start literture review

3D printing, formally additive manufacturing \citep{gibson2010additive} \citep{wong2012review}, has recently become state of the art technology which manufactures objects of complicated shapes with very high precision. It was developed in the 1980's \citep{kodama1981automatic} but recently it has been commercialised and is used in medical science \citep{kang20163d} and engineering \citep{wong2012review}. Because of such a wide range of applications, there has been a need for quality control and this can be done by scanning the 3D printed sample using x-ray computed tomography.

>>>>

One of the first methods of additive manufacturing (AM) is stereolithography \citep{kodama1981automatic, hull1986apparatus, 3d2019our} which involves the curing of a photosensitive resin using an ultraviolet laser. The technology has evolved and AM is capable of manufacturing objects with complicated internal and external geometries. However, there is a need for product inspection and in particular assessing the quality of the internal structures.

Imaging using x-rays \citep{rontgen1896on} have been used in the medical field. In x-ray computed tomography \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed}, the patent has an x-ray image taken at multiple angles. These x-ray images are used to reconstruct what was taken in 3D in order to make a diagnostic.

X-ray computed tomography (XCT) can be used as a non-destructive test for additive manufactured objects, this is the main theme of this thesis. Various reviews on additive manufacturing exist such as \cite{kruth1991material, kruth1998progress, pham1998comparison, gibson2010additive, wong2012review, ngo2018additive}. For XCT used in manufacturing, there are \cite{cantatore2011introduction, kruth2011computed, sun2012overview}. \cite{thompson2016x} reviewed the applications of XCT on AM.

In this chapter, AM is reviewed followed by XCT. The latest research for the use of XCT on AM is reviewed at the end of the chapter.

\section{Additive Manufacturing}

Loosely, AM involves solidifying material onto a moving platform so that the object is manufactured layer by layer. Typically this is a slow and expensive method compared to destructive methods such as drilling and cutting for example. However, this is not the full picture. The set up cost for AM is low, in particular destructive methods requires planning and setting up various apparatus before the manufacturing stage \citep{gibson2010additive}. This is why AM used to be called rapid prototyping \citep{kruth1991material}, it was suitable to manufacture bespoke items.

Various different AM technologies were invented during the advancement of AM. Because of this, there are various applications of AM, for example in medical and biomedical sciences \citep{kang20163d, kourra2018computed}, engineering \citep{cooper2015design}, food engineering \citep{godoi20163d} and art \citep{ornes2013mathematics, grossman2019bathsheba}.

\subsection{Additive Manufacturing Technologies}

The different AM technologies can be classified based on the apparatus, for example liquid based or power based, and/or on the method of manufacturing, for example point by point or layer by layer \citep{kruth1991material}. The liquid based AM technologies presented here are stereolithography \citep{kodama1981automatic, hull1986apparatus, 3d2019our} and fused deposition modelling \citep{crump1991fused, crump1992apparatus, stratasys2019what}. The following power based technologies are presented here: 3D printing \citep{sachs1990three}, selective laser sintering \citep{deckard1989method, dtm1990the, 3d2019our}, electron beam melting \citep{larsson2004arrangement, arcam2019history}, laser engineered net shaping \citep{atwood1998laser}.

Stereolithography is a liquid based AM technology. It consist of a container containing a liquid photo-hardening monomer or polymer as well as a piston and platform which holds and moves the manufactured product up and down. A laser with a specific wavelength, typically \SIrange{300}{400}{\nano\metre} \citep{kodama1981automatic}, is emitted onto a point of the surface of the liquid and solidifies. The laser is controlled by a computer to solidified specific parts of the liquid surface. The platform is lowered and the cycle repeats, manufacturing the object layer by layer. Laser absorption happens a few tenths of a millimetre which corresponds to the thickness of each layer \citep{kruth1991material, pham1998comparison}.

Fused deposition modelling is another liquid based AM technology. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in a form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer. The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer. In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.0001 inches (\SI{0.003}{\milli\metre}).

3D printing is a powder based AM technology. A jetting head deposit a binding agent in droplets onto a bed of powder of ceramic, metal or polymer. The binding agent is cured via evaporation or heating which glues the powder particles together. The bed can move in all 3 dimensions and the object is manufactured layer by layer. The binding agent must have low viscosity so it can be deposited, it may also be charged so that it can be deflected using an electric field for precise deposition \citep{sachs1990three}. The thickness of each layer is determined by the size of the droplets of the binding agent, which can be as small as \SI{15}{\micro\metre} in diameter \citep{sachs1990three}. \cite{sachs1990three} reported a tolerance of 0.001 inches (\SI{0.03}{\milli\metre}).

Selective laser sintering, electron beam melting and laser engineered net shaping are powder based AM technology. Selective laser sintering is similar to 3D printing but instead a laser is used to sinter or fuse the powder particles together. This is done in a chamber heated just below the melting point of the material \citep{wong2012review}. Various materials such as metal and plastics can be used \citep{wong2012review}. Electron beam melting is similar but instead an electron beam is used instead of a laser and this is done in a high vacuum chamber to avoid oxidation \citep{wong2012review}. In laser engineered net shaping, a powder bed is not used; instead the powder is deposited on the desired location and then melted using a laser. This is a popular method to manufacture metal objects \citep{gibson2010additive}.

There are many more AM technologies but they can be found in numerous review literatures. A comparison of the mentioned AM technologies available at the time were done by \cite{pham1998comparison, kim2008benchmark}. Factors such as material cost, mechanical properties and the resolution of the manufacturing were considered. There are also safety aspects to assess, for example powder in powder based methods can escape into the environment and the liquid used in stereolithography is toxic, sticky and has spilling risk \citep{kim2008benchmark}. This makes fused deposition modelling a popular choice and can be used in an office environment \citep{ngo2018additive}.

The strength of the manufactured object vary from geometry to geometry but also from direction to direction. Because the manufactured object was made layer by layer, the strength varies if the load was applied in the building direction (vertical) or the scanning direction (horizontal) \citep{kim2008benchmark}. Experimental results shown that fused deposition modelling has superior strength in the scanning direction but weak in the building direction \citep{kim2008benchmark}.

The strongest manufactured methods were found to be powder based methods and stereolithography, however they are slow and material costs are high \citep{kim2008benchmark}. Fused deposition modelling has low costs and high speeds but suffers from weak mechanical properties \citep{ngo2018additive}.

The materials available for each AM technology varies. The materials used in stereolithography is limited because of the use of liquids with photo-hardening properties \citep{ngo2018additive}. Fused deposition modelling is limited to plastics \citep{ngo2018additive}. Selective laser sintering and laser engineered net shaping can manufacture objects using metals such as aluminium alloys, steel, titanium and titanium alloys \citep{herzog2016additive}.

\subsection{Pre/Post Processing}

The blueprint of the object to be manufactured is called a computer-aided design (CAD). For it to be processed by an AM apparatus, the CAD is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces made up of series of triangles. STL stands for sterolithography but could also be called standard tessellation language \citep{wong2012review}. Some accuracy is lost here as the surface of the CAD is represented approximately by triangles \citep{gibson2010additive}. The STL file is then sliced into layers \citep{jamieson1995direct, vatani2009enhanced} so that the AM apparatus knows what to build for each layer.

When the AM object is manufactured, post processing techniques can be done at this stage. For example sanding may be done to smooth the surfaces \citep{gibson2010additive}. The manufactured object may be inspected for pores or defects by comparing the x-ray image of the object with the CAD \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}. This will be reviewed in the second half of this chapter.

As with any apparatus, regular maintenance is required \citep{bell2014maintaining}.

\subsection{Online Inspection and Defects}

The manufacturing process can be monitored, this is called online or in-situ process monitoring \citep{everton2016review}. The idea is that problems in the manufacturing is found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}.

There are various discontinuities in AM, in particular in the manufacturing of metal parts \citep{everton2016review}. For example gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}; they can be \SIrange{5}{20}{\micro\metre} in diameter \citep{everton2016review}. Layers may not fuse together and form elongated pores, this can be fixed by increasing the energy of the beam but too high will cause evaporation of the AM part \citep{mumtaz2008high}. They can be \SIrange{50}{500}{\micro\metre} in size \citep{everton2016review}. Low wetting ability of the melt pool can cause balling, this is where the sintered powder has poor contact on the existing layer causing spherical particles on the surface of the AM part \citep{li2012balling, gu2009balling}. The spherical particles can vary in size of \SIrange{10}{500}{\micro\metre} \citep{li2012balling}. Low oxygen content in the environment \citep{niu1999instability} and higher energy beams \citep{gu2009balling} can reduce the balling effect. Cracks can form due to extreme temperature changes and gradients \citep{mercelis2006residual, zaeh2010investigations}.

Various methods are used for in-situ process monitoring. Most commonly a high speed camera is installed capturing the various wavelengths in the electromagnetic spectrum emitted by the melt pool \citep{berumen2010quality, craeghs2011online, lott2011design}. Various discontinuities and errors can be detected \citep{clijsters2014in} and be used to give feedback to the AM apparatus \citep{herzog2013method}. Other methods include measuring the surface using a laser \citep{cerniglia2015inspection} and using an infrared camera to measure the temperature of the melt pool \citep{rodriguez2012integration}.
